---
title: 'rsat: handling multi-satellite images in R'
author: "U Pérez - Goya, M Montesino - SanMartin, A F Militino, and M D Ugarte"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
  word_document: default
documentclass: book
allow_html_dependencies: true
always_allow_html: true
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: ''
site: bookdown::bookdown_site
---

# Warn-Up

Package `rsat` provides tools for searching, managing, and processing, multi-satellite and multi-spectral data.

The `rsat` package is loaded by

```{r}
library(rsat)
```

The packages introduces two new R objects: `record` and `rtoi`. \#\# Instalation

```{r eval=FALSE}
# Install devtools package from cran repository
install.packages("devtools")

# load devtools library
library(devtools)

# Install RGISTools from GitHub repositoy
install_github("spatialstatisticsupna/rsat")
```

### Dependencies for linux

The package depends on some R packages that in Linux requires the installation of some libraries before the installation in R. Here you have the command to install all the applications from repository for Debian/Ubuntu and RedHat/Fedora.

#### Debian/Ubuntu

        sudo apt update
        sudo apt install r-cran-rcpp gdal-bin libgdal-dev libproj-dev libssl libssl-dev xml2 libxml2-dev libmagick++-dev

#### RedHat/Fedora

        sudo dnf install gdal gdal_devel proj_devel xml2 libxml2_devel libcurl_devel openssl_devel ImageMagick-c++_devel

## Sing Up credentials

The package can search images in different APIs. The support for multiple APIs requires multiple credentials.

### Modis

Credentials [EarthData](https://ers.cr.usgs.gov/register/)

### Landsat

Credentials [EarthData](https://ers.cr.usgs.gov/register/)

### Sentinel

Credentials [SciHub](https://scihub.copernicus.eu/dhus/#/self-registration)
